Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-17 index.Rmd
update buttons

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
load("bb_issuersTOOL.Rdata")
BUYBACK_DATA_TOOL$Industry_name <- as.character(BUYBACK_DATA_TOOL$Industry_name)

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

@@

```{r, eval=TRUE, echo = FALSE}
DATASET_NEW <- reactive({
  input$computeButton
  isolate({

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```

@@

feature_IRATStable <- reactive({
  input$computeButton
  isolate({

@@

feature_CALtable <- reactive({
  input$computeButton
  isolate({

@@

High_feature_Hedged_react <- reactive({
  input$computeButton
  isolate({

@@

Low_feature_Hedged_react <- reactive({
  input$computeButton
  isolate({

@@

<br> 
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
EU_index_table <- reactive({
  input$computeButton
  isolate({

@@

feature_IRATStable_industry <- reactive({
  input$computeButton
  isolate({

@@

feature_CALtable_industry <- reactive({
  input$computeButton
  isolate({

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
selected_features = reactive({
  input$computeButton
  isolate({

@@

Index_Score_rect <- reactive({
  input$computeButton
  isolate({

@@

feature_IRATStable_index <- reactive({
  input$computeButton
  isolate({

@@

feature_CALtable_index <- reactive({
  input$computeButton
  isolate({

@@

High_feature_Hedged_react_index <- reactive({
  input$computeButton
  isolate({

    thefeature = Index_Score_rect()
    High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
  })
})
Low_feature_Hedged_react_index <- reactive({
  input$computeButton
  isolate({

>>>>

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
load("bb_issuersTOOL.Rdata")

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButtonALL","Update Results",icon=icon("spinner")) )
```
<br>

@@

```{r, eval=TRUE, echo = FALSE}
DATASET_NEW <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  isolate({

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButtonALL2","Update Results",icon=icon("spinner")) )
```

@@

feature_IRATStable <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonindi

  isolate({

@@

feature_CALtable <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonindi

  isolate({

@@

High_feature_Hedged_react <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonindi

  isolate({

@@

Low_feature_Hedged_react <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonindi

  isolate({

@@

<br> 
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButtonindi","Update Results",icon=icon("spinner")) )
```
<br>

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButtonEU","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
EU_index_table <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonEU
  isolate({

@@

feature_IRATStable_industry <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonEU
  isolate({

@@

feature_CALtable_industry <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonEU
  isolate({

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButtonCU","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
selected_features = reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({

@@

Index_Score_rect <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({

@@

feature_IRATStable_index <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({

@@

feature_CALtable_index <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({

@@

High_feature_Hedged_react_index <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({

    thefeature = Index_Score_rect()
    High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
  })
})
Low_feature_Hedged_react_index <- reactive({
  input$computeButtonALL
  input$computeButtonALL2
  input$computeButtonCU
  isolate({
